Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-06-08 manuscript.tex
7 updates

Having an estimate of the RV that is more sensitive to stellar activity, like the mean of the SN, can help us to probe better stellar rotational periods, or understand better the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}. We saw in the preceding section that the RV estimated derived by the mean of the SN is 60\% noisier than the RV derived by the mean of the Normal. This is not necessarily a negative aspect. Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring SN mean RV, even if the white noise in the data is increased by 60\%.

Even if the different RV estimates have different amplitudes, once we apply our new correction for stellar activity, we arrive exactly to the same RV rms in the residuals, meaning that for an activity correction based on a linear combination of CCF parameters, the SN density fit does not help. We note that when comparing the activity correction presented in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, we only see a slight improvement brought by our proposed correction. We however encourage the community to use this new simple linear model if the goal is to reduce activity without considering the computationally expensive use of Gaussian Process. A further analysis of the p--value for each coefficient can be performed to see the ones that are not relevant and that can therefore be removed.

We checked if some RV estimates were better at finding planets in RV data affected by observed stellar signals. When using the new correction proposed in this paper to mitigate the effect from stellar activity, and when assesing planetary detection based on aperiodogram analysis, we find very similar detection limits for the three RV estimates presented in this paper. Therefore it seems that any of the RV estimate can be used to search for planetary signals.

Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN. It turns out that the mean of the SN should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than when taking the mean of the Normal distribution. However, the median of the SN should be used, as it is 10\% more precise than the mean of the Normal. Regarding the asymmetry estimates, we observe that $\gamma$ has a precision15\% better than the BIS SPAN. It is therefore clear in this case that the SN parameters are more precise to measure the RV and the asymmetry of the CCF.

>>>>

Having an estimator of RV that is more sensitive to stellar activity, such as the SN mean RV, can help with better probing stellar rotational periods or better understanding the covariance of stellar signals when fitting a Gaussian Process to the RVs \citep[e.g.][]{Faria-2016a, Haywood-2014}. 
We saw in the preceding section that the SN mean RV estimator is 60\% noisier than the N mean RV estimator. 
This is not necessarily a negative aspect. 
Indeed, in the case were photon-noise is not dominant, stellar activity can be better characterized if its effect can be amplified by measuring the SN mean RV, even if the white noise in the data is increased by 60\%. \jessi{white noise of the estimator?  The previous two sentences are not very convincing to me.}

Even if the different RV estimators generally have different amplitudes, once the new correction for stellar activity is applied, the residuals of the model have similar rms.  This suggests that for an activity correction based on a linear combination of CCF parameters, the SN density fit does not help. \jessi{The previous sentence does not seem to be a good sentence...I'm not sure what the intent of it is so I'm not sure how to fix it.}
When comparing the activity correction proposed in this paper with the usual correction that only uses a linear combination of the CCF asymmetry and width, there appears to be only a slight improvement. \jessi{In the previous sentence, are you referring to the real data only?  The SOAP data did show improvement - right?}
We however encourage the community to use this new simple linear model if the goal is to reduce activity without considering the computationally expensive use of Gaussian Process. \jessi{The previous sentence makes no sense given the discussion in this paragraph.  You are saying the proposed correction doesn't help, and then you say to use it...}
A further analysis of the p--value for each coefficient can be performed to see the ones that are not relevant and that can therefore be removed.

A test was carried out to see if some RV estimates were better at finding planets in RV data affected by observed stellar signals. 
When using the new correction proposed in this paper to mitigate the effect from stellar activity and when assessing planetary detection based on a periodogram analysis, we find very similar detection limits for the three RV estimators presented in this paper. 
\jessi{Maybe to try another test to see if the proposed correction is helpful, the detection-limit test could be carried out with the usual correction and we can see if it does not performa s well.}
Therefore it seems that any of the RV estimate can be used to search for planetary signals.

Finally, we investigated the precision of each of the SN and Normal parameters including the BIS SPAN. It turns out that the SN mean RV should not be used to get precise RVs as the standard errors on this parameter is 60\% greater than the N mean RV. 
However, the SN median RV is 10\% more precise than the N mean RV. 
Regarding the asymmetry estimates, we observe that $\gamma$ has a precision 15\% better than the BIS SPAN.
